---
title: "R Notebook"
output: html_notebook
---
# Loading Packages
```{r}
library(tidyverse)
```

# Load Data and do Inititial Overview
```{r}
income_df <- read.csv('adult.csv')
head(income_df)
```

```{r}
summary(income_df)
```

As seen everything is looking good, besides <capital.gain>, so I am going to check to see if there are any values other than 0

```{r}
income_df$capital.gain %>% unique()
```
My hunch was incorrect, however the data set on kaggle did not include any dictionaries or descriptions so I will take out the columns that does not make sense to me or have a clear title

```{r}
simp_df <- income_df %>% select(age, education, marital.status, occupation, relationship, race, sex, hours.per.week, native.country, income)
```

# Data Cleaning
From the looks of it the only column I'd like to change is occupation as "?" seems a little vague so I will just change it to "Occupation not specified"
```{r}
simp_df$occupation[simp_df$occupation == "?"] <- "Occupation not specified"
simp_df$occupation %>% unique()
```
Nice! Looks like we got rid of the "?"!

# Data Visualization
Now time to visualize the data and see which variable have a strong relationship with income.
First I'll do
```{r}
simp_df %>% 
  select(age, income) %>% 
  mutate(age_bin = 
           cut(age, breaks = 4)) %>% 
  group_by(age_bin, income) %>% 
  count() %>% 
  ggplot(aes(x = age_bin, fill = income, y = n)) +
  geom_bar(position = 'dodge', stat = 'identity')
```

